Meta-analysis of composite outcomes in clinical trials

### 2025-01-29 MSc_poster_template.Rmd
Update MSc_poster_template.Rmd

EMERGE_background_stats <- data.frame(t(as.matrix(EMERGE_background_stats)))
knitr::kable(EMERGE_background_stats, caption = 'EMERGE *p*-values', align = 'c', format = "html") %>%
  kable_styling(font_size = 20) %>%
  add_header_above(c("Primary Composite Outcome N/total (%)" = 2, " " = 1))
```

>>>>

EMERGE_background_stats <- data.frame(t(as.matrix(EMERGE_background_stats)))
knitr::kable(EMERGE_background_stats, caption = 'EMERGE *p*-values', align = 'c', format = "html") %>%
  kable_styling(font_size = 20) %>%
  add_header_above(c("Primary Composite Outcome N/total (%)" = 2, " " = 1))
```
# Analysis of EMERGE DATA SET
The primary composite outcome at 32 and 38 weeks was not significantly different between the **metformin group (154 of 264) and the placebo group (82 of 262)**. This lack of significance is indicated by a **risk difference of -6.9%** (95% CI, -15.1% to 1.4%) and a**relative risk of 0.89** (95% CI, 0.78 to 1.02).
